---
title: 'OMCA - A/B Testing: Wishlist vs. Basket (= t-test)'
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the data

```{r}
## Basic setup ##
rm(list = ls())



## Load Data ##
data <- read.csv("https://raw.githubusercontent.com/Damanpreet7/A-B-Testing/main/OMCA_AB-Test_Data.csv", header=TRUE, sep=";")
```

head(data)

## Calculate Metrics: Open Rate & Click-through-rate
```{r}
data$OR <- data$Open / data$Sent * 100
data$CTR <- data$Click / data$Sent * 100
```

## Looking at the data
```{r}
plot(density(data$OR), main="Density: OR")
plot(density(data$CTR), main="Density: CTR")
```

## Visually Comparing Open and Click Through Rates

We will be using the "ggplot" package throughout this course. This is a very (if not the most) commonly used and helpful tool for visualization. 

```{r, results='asis'}

# Load the package
library(ggplot2)

# Plot for OR
plot_or <- ggplot(data, aes(x=Group, y=OR)) +
  stat_summary(fun=mean, geom="bar") +
  stat_summary(aes(label=round(..y..,2)), fun=mean, geom="text", size=4, vjust = -0.5) +
  labs(title="Open Rate by Campaign",
       x ="Campaign", y = "Open Rate (in %)") +
  theme_light() +
  coord_cartesian(ylim = c(0,45))
plot_or

# Plot for CTR
plot_ctr  <- ggplot(data, aes(x=Group, y=CTR)) +
  stat_summary(fun=mean, geom="bar") +
  stat_summary(aes(label=round(..y..,2)), fun=mean, geom="text", size=4, vjust = -0.5) +
  labs(title="Click Through Rate by Campaign",
       x ="Campaign", y = "Click Through Rate (in %)") +
  theme_light() +
  coord_cartesian(ylim = c(0,45))
plot_ctr

# Plotting Results besides each other: Package "ggpubr" might take some time to install
library(ggpubr)
ggarrange(plot_or, plot_ctr, 
          labels = c("A", "B"),
          ncol = 2, nrow = 1)
```

## Advanced: comparing density distributions by group
```{r}
# Plot Density OR
plot_density_or <- ggplot(data, aes(x=OR, fill=Group))+
  geom_density(alpha=0.4) + 
  xlim(20, 60) +
  labs(fill = "Campaign") +
  labs(title="Open Rate by Campaign", 
       x="OR (in %)", y = "Density") +
  theme_light() + 
  theme(legend.position="bottom")

# Plot Density CTR
plot_density_ctr <- ggplot(data, aes(x=CTR, fill=Group))+
  geom_density(alpha=0.4) + 
  xlim(0, 20) +
  labs(fill = "Campaign") +
  labs(title="Click Through Rate by Campaign", 
       x="CTR (in %)", y = "Density") +
  theme_light() + 
  theme(legend.position="bottom")

# Combine
ggarrange(plot_density_or, plot_density_ctr, 
          labels = c("A", "B"),
          ncol = 2, nrow = 1)
```


## Statistically Comparing Open and Click Through Rates

```{r}
#Open Rate
t.test(OR ~ Group, data)

# Click-Through-Rate
t.test(CTR ~ Group, data)
```


## Alternative: Use Regression instead of a t-test
```{r}
r1 <- lm(OR ~ Group, data)
summary(r1)
r2 <- lm(CTR ~ Group, data)
summary(r2)
```
